%-----------------------------------------------------------------------
\ifenglish
\section{Simple prompt dialog}
\else
\section{диалог Simple prompt}
\fi
\public{ASKTEXT\_DIALOG}

\begin{popup}
\caption{Simple prompt}
\public{ASKTEXT\_EDIT}
\public{ASKTEXT\_PROMPT}
\public{ASKTEXT\_OK}
\public{ASKTEXT\_CANCEL}

\ifenglish
The Environment displays this dialog whenever it has to prompt you for
a single string value, e.g. a line number. Type a value in the entry field
and select the {\bf OK} pushbutton.

Select the {\bf Cancel} pushbutton if you decided not to perform an action.
\else
Оболочка выводит этот диалог всякий раз, когда ей необходимо запросить
у вас одно строковое значение, иначе говоря, номер строки. Наберите значение в
поле ввода и нажмите кнопку {\bf OK}.

Нажмите кнопку {\bf Cancel}, если решили не производить операцию.
\fi
\end{popup}

%-----------------------------------------------------------------------

\ifenglish
\section{About dialog}
\else
\section{диалог About}
\fi
\public{ABOUT\_DIALOG}

\ifenglish
XDS version and copyright information is displayed in this dialog
along with a set of system parameters.

Select the {\bf OK} pushbutton to dismiss the dialog.
\else
В этом диалоге отображена версия XDS и патентная информация вместе с рядом
системных параметров

Нажмите {\bf OK}, чтобы закрыть диалог. 
\fi
%-----------------------------------------------------------------------

\ifenglish
\section{Printing dialog}
\else
\section{диалог Printing}
\fi
\public{PRINTABORT\_DIALOG}

\ifenglish
Select the {\bf Cancel} pushbutton to interrupt printing.
\else
Нажмите кнопку {\bf Cancel}, чтобы прервать печать.
\fi
%-----------------------------------------------------------------------

\begin{popup}
\caption{OK}
\public{IDOK}

\ifenglish
Select the {\bf OK} pushbutton to confirm the changes you made
in a dialog box and/or perform an action.
\else
Нажмите кнопку {\bf OK}, чтобы подтвердить изменения, которые вы произвели
и/или чтобы выполнить операцию.
\fi
\end{popup}

\begin{popup}
\caption{Cancel}
\public{IDCANCEL}

\ifenglish
Select the {\bf Cancel} pushbutton if you decide to undo
your changes and/or not to perform an action.
\else
Нажмите кнопку {\bf Cancel}, если решили не производить изменений и/или
не производить операцию.
\fi
\end{popup}

\begin{popup}
\caption{Help}
\public{IDHELP}

\ifenglish
Select the {\bf Help} pushbutton to display the on-line help for
the active dialog.
\else
Нажмите кнопку {\bf Help}, чтобы вывести текущую помощь по активному диалогу.
\fi
\end{popup}

%-----------------------------------------------------------------------
